Plot density of imputations

### 2020-02-26 3.Thesis/plot_imputation_densities.Rmd
same with different data

```{r echo=TRUE, message=FALSE, warning=FALSE}
# set-up environment
library(mice) # Data imputation
library(dplyr) # Data manipulation
# library(magrittr)
# library(broom)
library(ggplot2)
library(purrr)
set.seed(123)
dat <- nhanes

# parameters
M <- 20
T_max <- 10

@@

@@

#sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot() + geom_line(aes(x = nr_it, y = sd)) + facet_wrap(~case)
sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot(aes(x = nr_it, y = sd, col = case)) + geom_line() + geom_smooth(se = F)

@@

Now for any variable
```{r}
# objects
imputed_values <- plot <- distr <- list()

# which vars?
nmis <- dat %>% map_dbl(~{is.na(.x) %>% sum()}) #%>% which(.>0) %>% names()
#nmis <- apply(is.na(dat), 2, sum)
vars <- names(nmis[nmis>0])

@@

imputed_values[[1]]$bmi %>% mutate(case = row_number())
#map(imputed_values, function(x) map(vars, function(y) {print(x)}))#mutate(case = row_number())})) #%>%  tidyr::gather("imp", "value", 1:M) %>% .[order(.$case, .$imp),]}) 
test5 <- map(imputed_values, function(x) map(x, function(y) {as.data.frame(y) %>% mutate(case = row_number()) %>%  tidyr::gather("imp", "value", 1:M)}))  #%>% .[order(.$case, .$imp),]}) })) 
# case_mean <- imputed_values %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))

>>>>

```{r echo=TRUE, message=FALSE, warning=FALSE}
# set-up environment
library(mice) # Data imputation
library(dplyr) # Data manipulation
# library(magrittr)
# library(broom)
library(ggplot2)
library(purrr)
set.seed(123)
dat <- boys

# parameters
M <- 20
T_max <- 50

@@

# this should be repeated T times
for (it in 1:T_max) {
  if (it == 1) {
    # impute missingness with one iteration
    mids <- mice(dat,
                 maxit = 1,
                 #method = "norm",
                 m = M,
                 print = FALSE)
  } else {
    # add an iteration
    mids <- mice.mids(mids, maxit = 1, printFlag = FALSE)
  }

@@

#sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot() + geom_line(aes(x = nr_it, y = sd)) + facet_wrap(~case)
sd_per_case_per_it %>%  tidyr::gather("case", "sd", 1:9) %>% ggplot(aes(x = nr_it, y = sd, col = case)) + geom_point() + geom_smooth(se = F)

@@

Now for any variable, for one iteration nr. only.
```{r}
# which vars?
# only numeric
num_vars <- dat %>% map(~{is.numeric(.x)})
dat <- dat[,num_vars==T]
# only with missings
nmis <- dat %>% map_dbl(~{is.na(.x) %>% sum()}) #%>% which(.>0) %>% names()
#nmis <- apply(is.na(dat), 2, sum)
vars <- names(nmis[nmis>0])

# extract imputed values, reshape data
imp_long <- mids[["imp"]][vars] %>% map( ~{
  mutate(., case = rownames(.)) %>%  tidyr::gather("imp", "value", 1:M)
  })

# compute mean and sd for each case
imp_descr <- imp_long %>% map( ~{
  group_by(., case) %>% summarise(mu = mean(value), sigma = sd(value), sd1 = mu+sigma, sd2 = mu-sigma)
})

# plot each case with mean and sd per variable
map2(imp_long, imp_descr, ~{
  ggplot(.x, aes(x = value)) +
    geom_histogram() +
    geom_vline(.y, mapping = aes(xintercept = mu)) +
    geom_vline(.y, mapping = aes(xintercept = sd1), linetype = "dotted") +
    geom_vline(.y, mapping = aes(xintercept = sd2), linetype = "dotted") +
    ggtitle("Distribution of imputed values per case (mean and 1 SD indicated)") +
    #xlab(.y) +
    facet_wrap( ~ case)
})

Now try to automate this for all nrs of iterations
```{r eval=FALSE, include=FALSE}
# objects
imputed_values <- plot <- distr <- list()

@@

imputed_values[[1]]$bmi %>% mutate(case = row_number())
#map(imputed_values, function(x) map(vars, function(y) {print(x)}))#mutate(case = row_number())})) #%>%  tidyr::gather("imp", "value", 1:M) %>% .[order(.$case, .$imp),]}) 
test5 <- map(imputed_values, function(.x) map(.x, function(.y) {as.data.frame(.y) %>% mutate(case = row_number()) %>%  tidyr::gather("imp", .y, 1:M)  %>% .[order(.$case),] %>% mutate(.x = .$value) }))#group_by(.$case) %>% summarise(mu = mean(.$value), sigma = sd(.$value))}) ) 
# case_mean <- imputed_values %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))
# test5[[1]]$bmi %>% group_by(case) %>% summarise(mu = mean(value), sigma = sd(value))

#test5[[1]] %>% map(function(x) map(x, function(y) {rename(., y = .$value)}))
